---
title: "050423-segura-meeting.Rmd"
output: html_document
date: "2023-04-05"
---

WARNING: THIS NOTEBOOK IS SPECFIC TO EPIDERMIS for simplicity. a different notebook will address dermis

## 0a. load libraries
```{r, load}
library(tidyverse)
library(dplyr)

conversion = 100/22  #write multiplication conversion factor here; currently holds test value
```


## 0b. Read in the epidermis and dermis pixel dataframes 
skip first column (it is just the number of rows)
```{r, open-dermis-and-epidermis-dfs}
all_epidermis <- read_csv(paste0("../data/","all_epidermis_lengths_in_pixels.csv"))
a<-length(colnames(all_epidermis))

all_dermis <- read_csv(paste0("../data/","all_dermis_lengths_in_pixels.csv"))
b<-length(colnames(all_dermis))

# skip first column (it is just the number of rows)
all_epidermis <- all_epidermis[,2:a]
all_dermis <- all_dermis[,2:b]

# apply conversion
all_epidermis_micron <- all_epidermis/conversion
all_dermis_micron <- all_dermis/conversion
```

## 0c. Rename epidermis and dermis df for readability
```{r, load-pixel-epiderm-derm}
all_dermis_lengths_in_pixels <- all_dermis
all_epidermis_lengths_in_pixels <- all_epidermis

all_dermis_lengths_in_microns <- all_dermis_micron
all_epidermis_lengths_in_microns <- all_epidermis_micron
```


## 1. visualize spread of each animal's EPIDERMIS lengths...
- use same binwidth and same axes
```{r, spread-epi-micron-data}
df_set1<-all_epidermis_lengths_in_microns[,1:6]
df_set2<-all_epidermis_lengths_in_microns[,7:12]
df_set3<-all_epidermis_lengths_in_microns[,13:18]
df_set4<-all_epidermis_lengths_in_microns[,19:24]
df_set5<-all_epidermis_lengths_in_microns[,25:30]

# convert data to long format using tidyr::pivot_longer()
long1 <- tidyr::pivot_longer(df_set1, everything())
long2 <- tidyr::pivot_longer(df_set2, everything())
long3 <- tidyr::pivot_longer(df_set3, everything())
long4 <- tidyr::pivot_longer(df_set4, everything())
long5 <- tidyr::pivot_longer(df_set5, everything())
```

### 1a. on scale of 0-125 microns
```{r, spread-epi-micron-histgraph}
# set y-axis range
x_range <- c(0,125)

# plot using ggplot and facet_wrap()
p1<-ggplot(long1[], aes(x = value)) +
  geom_histogram(color="black", fill="white", binwidth = 2) +
  facet_wrap(~ name, scales = "fixed") +
  labs(x = "Pixel Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text())
p1
#ggsave("animal-pixel-lenght-spread1.jpg", plot = p1, dpi = 300, width = 6, height = 4, units = "in")

p2<-ggplot(long2[], aes(x = value)) +
  geom_histogram(color="black", fill="white", binwidth = 2) +
  facet_wrap(~ name, scales = "fixed") +
  labs(x = "Pixel Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text())
p2
#ggsave("animal-pixel-lenght-spread2.jpg", plot = p2, dpi = 300, width = 6, height = 4, units = "in")

p3<-ggplot(long3[], aes(x = value)) +
  geom_histogram(color="black", fill="white", binwidth = 2) +
  facet_wrap(~ name, scales = "fixed") +
  labs(x = "Pixel Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text())
p3
#ggsave("animal-pixel-lenght-spread3.jpg", plot = p3, dpi = 300, width = 6, height = 4, units = "in")

p4<-ggplot(long4[], aes(x = value)) +
  geom_histogram(color="black", fill="white", binwidth = 2) +
  facet_wrap(~ name, scales = "fixed") +
  labs(x = "Pixel Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text())
p4
#ggsave("animal-pixel-lenght-spread4.jpg", plot = p4, dpi = 300, width = 6, height = 4, units = "in")

p5<-ggplot(long5[], aes(x = value)) +
  geom_histogram(color="black", fill="white", binwidth = 2) +
  facet_wrap(~ name, scales = "fixed") +
  labs(x = "Pixel Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text()) 
p5
#ggsave("animal-pixel-lenght-spread5.jpg", plot = p5, dpi = 300, width = 6, height = 4, units = "in")
```

```{r, spread-epi-micron-densitygraph}
# set y-axis range
x_range <- c(0,125)

# plot using ggplot and facet_wrap()
p1<-ggplot(long1[], aes(x = value)) +
  geom_density(color="black", fill="darkgrey") +
  facet_wrap(~ name, scales = "fixed") +
   theme_minimal()+
  labs(x = "Pixel Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text())
p1
#ggsave("../visualizations/shape-center-spread/epiderm/all_animals-micron-length-spread1.jpg", plot = p1, dpi = 300, width = 6, height = 4, units = "in")

p2<-ggplot(long2[], aes(x = value)) +
  geom_density(color="black", fill="darkgrey") +
  facet_wrap(~ name, scales = "fixed") +
   theme_minimal()+
  labs(x = "Pixel Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text())
p2
#ggsave("../visualizations/shape-center-spread/epiderm/all_animals-micron-length-spread2.jpg", plot = p2, dpi = 300, width = 6, height = 4, units = "in")

p3<-ggplot(long3[], aes(x = value)) +
  geom_density(color="black", fill="darkgrey") +
  facet_wrap(~ name, scales = "fixed") +
   theme_minimal()+
  labs(x = "Pixel Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text())
p3
#ggsave("../visualizations/shape-center-spread/epiderm/all_animals-micron-length-spread3.jpg", plot = p3, dpi = 300, width = 6, height = 4, units = "in")

p4<-ggplot(long4[], aes(x = value)) +
  geom_density(color="black", fill="darkgrey") +
  facet_wrap(~ name, scales = "fixed") +
   theme_minimal()+
  labs(x = "Pixel Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text())
p4
#ggsave("../visualizations/shape-center-spread/epiderm/all_animals-micron-length-spread4.jpg", plot = p4, dpi = 300, width = 6, height = 4, units = "in")

p5<-ggplot(long5[], aes(x = value)) +
  geom_density(color="black", fill="darkgrey") +
  facet_wrap(~ name, scales = "fixed") +
   theme_minimal()+
  labs(x = "Pixel Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text())
p5
#ggsave("../visualizations/shape-center-spread/epiderm/all_animals-micron-length-spread5.jpg", plot = p5, dpi = 300, width = 6, height = 4, units = "in")
```

### 1b. zoom in on select graphs
Only one graph example is shown
```{r warning=FALSE}

# plot using ggplot
# variables that chaneg are `long*[]` and `Animal_*`
targetAnimal_only <- long1[] %>% filter(startsWith(name, "Animal_A."))

p1<-ggplot(targetAnimal_only, aes(x = value)) +
  geom_density(fill = "blue", alpha = 0.5) +
  theme_minimal()+
  facet_wrap(~ name, scales = "fixed") +
  labs(x = "Pixel Value", y = "Frequency")+
  scale_x_continuous(limits = c(0,125), expand = c(0, 0))+
  theme(axis.title.x = element_text())
  ggsave("../visualizations/shape-center-spread/epiderm/Animal_A-micron-length-spread-zoomedView.jpg", plot=p1, dpi = 300, width = 6, height = 4, units = "in")

p2<-ggplot(targetAnimal_only, aes(x = value)) +
  geom_density(fill = "grey", color="transparent", alpha = 0.5) +
  theme_minimal()+
  facet_wrap(~ name, scales = "fixed") +
  labs(x = "Pixel Value", y = "Frequency")+
  scale_x_continuous(limits = c(0,125), expand = c(0, 0))+
  theme(axis.title.x = element_text())
  ggsave("../visualizations/shape-center-spread/epiderm/Animal_A-micron-length-spread-standardView.jpg", plot=p2, dpi = 300, width = 6, height = 4, units = "in")

```

## 3. FUNCTIONS for calculating metrics 

### 3a. Write funciton to unblind animal identities
```{r, unblind-fnc}
add_identity_unblind_column <- function(df) {
  # Define a lookup table of filename prefixes and corresponding identity_unblind values
  prefixes <- c("Animal_A" = "Exp17_Racemic-MAP_POD7_Mouse14",
                "Animal_C" = "Exp16_D-MAP_POD4_Mouse3",
                "Animal_D" = "Exp15_L-MAP_Mouse3_POD4",
                "Animal_F" = "Exp17_Racemic-MAP_POD7_Mouse11",
                "Animal_H" = "Exp17_Racemic-MAP_POD4_Mouse2",
                "Animal_I" = "Exp15_L-MAP_POD7_Mouse13",
                "Animal_J" = "Exp15_L-MAP_POD4_Mouse2",
                 "Animal_O" = "Exp17_Racemic-MAP_POD7_Mouse13",
                "Animal_W" = "Exp17_Racemic-MAP_POD7_Mouse12",
                "Animal_X" = "Exp14_No-MAP_POD4_Mouse2",
                #"Animal_Y" = "Exp16_D-MAP_POD7_Mouse11",
                "Animal_Z1" = "Exp17_Racemic-MAP_POD4_Mouse1",
                "Animal_B" = "Exp15_POD7_Mouse11_L-MAP",
                "Animal_P" = "Exp14_POD7_Mouse13_D-MAP",
                #"Animal_R" = "Exp16_POD7_Mouse2_D-MAP",
                "Animal_Z6" = "Exp16_POD7_Mouse11_D-MAP",
                "Animal_Z8" = "Exp16_POD4_Mouse2_D-MAP",
                 #"Animal_Z3" = "Exp15_Mouse12_POD7_LMAP",
                "Animal_Z9" = "Exp17_POD4_Mouse3_Racemic-MAP",
                "Animal_Z10" = "Exp16_POD4_Mouse1_D-MAP",
               
                "Animal_E" = "Exp14_No-MAP_POD7_Mouse11",
                "Animal_K" = "Exp14_No-MAP_POD4_Mouse4",
                "Animal_L" = "Exp14_No-MAP_POD7_Mouse12",
                "Animal_M" = "Exp14_No-MAP_POD4_Mouse3",
                "Animal_U" = "Exp14_No-MAP_POD4_Mouse1",
                "Animal_Z2" = "Exp14_POD7_Mouse14_No-MAP",
                "Animal_Z4" = "Exp15_POD4_Mouse1",
                
                "Animal_G" = "Unmanipulated_PepB",
                "Animal_N" = "Unmanip_PepB",
                "Animal_V" = "Unmanip_B6",
                "Animal_Z" = "UnmanipB6")
                
                
  
  # Use sapply to look up the identity_unblind value for each filename in the dataframe
  df$identity_unblind <- sapply(df$filename, function(x) {
    prefix <- substr(x, 1, 8) # Extract the first 8 characters of the filename
    prefixes[prefix] # Look up the corresponding identity_unblind value
  })
  
  return(df)
}

```

### 3b. Write function to calculate sd of length for each column (aka each animal) 
```{r, fnc-to-calc-sd}
calculate_sd <- function(data) {
  # Calculate column-wise sd using sapply function
  std_deviations <- apply(data, 2, sd, na.rm = TRUE)
  
  # Create a new dataframe to store the column-wise averages
  sd_df <- data.frame(column = names(data), sd = std_deviations)
  
  # Return the new dataframe
  return(sd_df)
}
```

### 3b. Write function to calculate range (max-min) of length for each column (aka each animal) 
```{r, fnc-to-calc-sd}
calculate_range <- function(data) {
  
 range_ <- function(vector){
   na_rm_values <- vector[!is.na(vector)]
    if (length(na_rm_values) <= 1) {
      return(NA)
    } else {
      return(max(na_rm_values) - min(na_rm_values))
    }
 }
 
  ranges <- apply(data, 2, range_)
  
  # Create a new dataframe to store the column-wise averages
  range_df <- data.frame(column = names(data), range = ranges)
  
  # Return the new dataframe
  return(range_df)
}

# first remove the NA values from each column using !is.na(x) and store non-NA values in na_rm_values 
# If there are at least two non-NA values  calculate the maximum minus the minimum using max(na_rm_values) - min(na_rm_values) otherwise return NA for that column.
```


### 3c. Write function to calculate average length for each column in epidermis and dermis dfs (aka each animal)
```{r, fnc-to-calcualte-averages}
# Define a function to calculate column-wise averages
calculate_averages <- function(data) {
  # Calculate column-wise averages using colMeans() function
  avg <- colMeans(data, na.rm = TRUE)
  
  # Create a new dataframe to store the column-wise averages
  avg_df <- data.frame(column = names(data), average = avg)
  
  # Return the new dataframe
  return(avg_df)
}

```

## 4. Use previous function to create dataframes for all metrics

### 4a. make df for SD's for each animal lengths
```{r, calc-averages}
# Call the calculate_averages() function to calculate the column-wise averages
all_epidermis_in_pixels_AVG <- calculate_averages(all_epidermis_lengths_in_pixels)
colnames(all_epidermis_in_pixels_AVG)<-c("filename", "average")
rownames(all_epidermis_in_pixels_AVG)<-c(1:length(rownames(all_epidermis_in_pixels_AVG)))

all_dermis_in_pixels_AVG <- calculate_averages(all_dermis_lengths_in_pixels)
colnames(all_dermis_in_pixels_AVG)<-c("filename", "average")
rownames(all_dermis_in_pixels_AVG)<-c(1:length(rownames(all_epidermis_in_pixels_AVG)))
```

### Visualize average pixel lengths (per animal) for epidermis/dermis 
Use bar chart
```{r, viz-animal-pixel-averages}
categories <- c(letters[1:16], "r", "u", "v", "w", "x", "y", "z", "z1", "z10", "z2", "z4", "z6", "z8", "z9")

# for epidermis
df1<- cbind(all_epidermis_in_pixels_AVG, categories)
p1<-ggplot(df1, aes(x = categories, y = all_epidermis_in_pixels_AVG[,2])) +
  geom_bar(stat = "identity", color="black", fill="white") +
  xlab("Animal") +
  ylab("Average Length of Epidermis in pixels")
p1

ggsave("avg-epidermis-pixel-length-by-animal.jpg", plot = p1, dpi = 300, width = 6, height = 4, units = "in")

# for dermis
df2<- cbind(all_dermis_in_pixels_AVG, categories)
p2<-ggplot(df2, aes(x = categories, y = all_epidermis_in_pixels_AVG[,2])) +
  geom_bar(stat = "identity", color="black", fill="white") +
  xlab("Animal") +
  ylab("Average Length of Dermis in pixels")
p2

ggsave("avg-dermis-pixel-length-by-animal.jpg", plot = p2, dpi = 300, width = 6, height = 4, units = "in")
```


### save blinded average pixel length df's for epidermis and dermis
```{r, save-blind-avg-pixel-dermis-and-epidermis-dfs}
## ONLY RUN IF DATAFRAMS NOT ALREADY SAVED!

write.csv(df1, file=paste0("../data/","blind_avg_epidermis_lengths_in_pixels.csv"))
write.csv(df2, file=paste0("../data/","blind_avg_dermis_lengths_in_pixels.csv"))
```



### Use previous function to unblind epidermis and dermis df's
```{r, use-unblind-fnc}
unblind_all_epidermis_in_pixels_AVG <- add_identity_unblind_column(all_epidermis_in_pixels_AVG)

unblind_all_dermis_in_pixels_AVG <- add_identity_unblind_column(all_dermis_in_pixels_AVG)
```

### save the unblind epidermis and dermis dfs
```{r, save-ublinded-dfs}
# ONLY RUN IF THESE DF's AREN'T ALREADY SAVED!!
write.csv(unblind_all_epidermis_in_pixels_AVG, file=paste0("../data/","unblind_avg_epidermis_lengths_in_pixels.csv"))

write.csv(unblind_all_dermis_in_pixels_AVG, file=paste0("../data/","unblind_avg_dermis_lengths_in_pixels.csv"))
```

### Prism graphs
#### Write function to filter data for prism
```{r, filter-prism-fnc}
# get only the unmanip
filter_data_by_phrase <- function(df, phrase) {
  filtered_df <- df[grep(phrase, df$identity_unblind), ]
  return(filtered_df)
}

# This function takes two parameters: df, which is the data frame to be filtered, and phrase, which is the phrase to search for in the "identity_unblind" column. The grep() function is used to search for the given phrase in the "identity_unblind" column, and the resulting indices are used to subset the original data frame.
```

#### Wrtie fucntion to deal with different lengths for filtered data made for prism
```{r, df-length-fnc}
create_dataframe <- function(vec1, vec2, vec3, vec4, vec5) {
  # Get the maximum length of the vectors
  max_length <- max(length(vec1), length(vec2), length(vec3), length(vec4), length(vec5))
  
  # Pad shorter vectors with NAs
  vec1 <- c(vec1, rep(NA, max_length - length(vec1)))
  vec2 <- c(vec2, rep(NA, max_length - length(vec2)))
  vec3 <- c(vec3, rep(NA, max_length - length(vec3)))
  vec4 <- c(vec4, rep(NA, max_length - length(vec4)))
  vec5 <- c(vec5, rep(NA, max_length - length(vec5)))
  
  # Create the data frame
  df <- data.frame(vec1, vec2, vec3, vec4, vec5)
  return(df)
}

```

#### Use the previous two functions to filter data for prism part 1
```{r, use-filter-prism-fnc}
p1<- "Unmanip"
p2<-"No-MAP"
p3<-"L-MAP"
p4<-"D-MAP"
p5<-"Racemic-MAP"

# for epiderm

# deal with different lengths
all_epidermal_pixel_thickness_prismDf<-create_dataframe((filter_data_by_phrase(unblind_all_epidermis_in_pixels_AVG, p1))$average,
      (filter_data_by_phrase(unblind_all_epidermis_in_pixels_AVG, p2))$average,
      (filter_data_by_phrase(unblind_all_epidermis_in_pixels_AVG, p3))$average,
      (filter_data_by_phrase(unblind_all_epidermis_in_pixels_AVG, p4))$average,
      (filter_data_by_phrase(unblind_all_epidermis_in_pixels_AVG, p5))$average)
colnames(all_epidermal_pixel_thickness_prismDf) <- c("NonOp", "No MAP", "L-MAP", "D-MAP", "R-MAP")
View(all_epidermal_pixel_thickness_prismDf)

# for derm
all_dermal_pixel_thickness_prismDf<-create_dataframe((filter_data_by_phrase(unblind_all_dermis_in_pixels_AVG, p1))$average,
      (filter_data_by_phrase(unblind_all_dermis_in_pixels_AVG, p2))$average,
      (filter_data_by_phrase(unblind_all_dermis_in_pixels_AVG, p3))$average,
      (filter_data_by_phrase(unblind_all_dermis_in_pixels_AVG, p4))$average,
      (filter_data_by_phrase(unblind_all_dermis_in_pixels_AVG, p5))$average)
colnames(all_dermal_pixel_thickness_prismDf) <- c("NonOp", "No MAP", "L-MAP", "D-MAP", "R-MAP")
View(all_dermal_pixel_thickness_prismDf)
```

#### save the prism df's made in the previous chunk
```{r, save-prism-dfs}
# ONLY RUN IF THESE DF's AREN'T ALREADY SAVED!!
write.csv(epidermal_thickness_prismDf, file=paste0("../data/","all_epidermal_pixel_thickness_prismDf.csv"))

write.csv(dermal_thickness_prismDf, file=paste0("../data/","all_dermal_pixel_thickness_prismDf.csv"))
```

#### export to github for prism part 1
Run the following in terminal
git add ../data/all_epidermal_pixel_thickness_prismDf.csv 
git add ../data/all_dermal_pixel_thickness_prismDf.csv 
git commit -m "add prism part1 file"
git push

Then go to github and copy paste into excel
Then copy and past into prism


#### Use the previous two functions to filter data for prism part 2 (POD4 & POD7)
When copyign and pasting remember to exclude 1st column which is placeholder repeat
```{r, use-filter-prism-fnc}
p2<-"No-MAP"
p3<-"L-MAP"
p4<-"D-MAP"
p5<-"Racemic-MAP"

# POD4----------------------
# for epiderm
#first filter by pod4
df1<-filter_data_by_phrase(unblind_all_epidermis_in_pixels_AVG, "POD4")

# deal with different lengths
pod4_epidermal_pixel_thickness_prismDf<-create_dataframe(
      c(NA),
      (filter_data_by_phrase(df1, p2))$average,
      (filter_data_by_phrase(df1, p3))$average,
      (filter_data_by_phrase(df1, p4))$average,
      (filter_data_by_phrase(df1, p5))$average)
colnames(pod4_epidermal_pixel_thickness_prismDf) <- c("don't copy this column","No MAP", "L-MAP", "D-MAP", "R-MAP")
View(pod4_epidermal_pixel_thickness_prismDf)

# for derm
#first filter by pod4
df2<-filter_data_by_phrase(unblind_all_dermis_in_pixels_AVG, "POD4")

# deal with different lengths
pod4_dermal_pixel_thickness_prismDf<-create_dataframe(
      c(NA),
      (filter_data_by_phrase(df2, p2))$average,
      (filter_data_by_phrase(df2, p3))$average,
      (filter_data_by_phrase(df2, p4))$average,
      (filter_data_by_phrase(df2, p5))$average)
colnames(pod4_dermal_pixel_thickness_prismDf) <- c("don't copy this column", "No MAP", "L-MAP", "D-MAP", "R-MAP")
View(pod4_dermal_pixel_thickness_prismDf)

# POD7----------------------
# for epiderm
#first filter by pod4
df1<-filter_data_by_phrase(unblind_all_epidermis_in_pixels_AVG, "POD7")

# deal with different lengths
pod7_epidermal_pixel_thickness_prismDf<-create_dataframe(
      c(NA),    
      (filter_data_by_phrase(df1, p2))$average,
      (filter_data_by_phrase(df1, p3))$average,
      (filter_data_by_phrase(df1, p4))$average,
      (filter_data_by_phrase(df1, p5))$average)
colnames(pod7_epidermal_pixel_thickness_prismDf) <- c("don't copy this column","No MAP", "L-MAP", "D-MAP", "R-MAP")
View(pod7_epidermal_pixel_thickness_prismDf)

# for derm
#first filter by pod4
df2<-filter_data_by_phrase(unblind_all_dermis_in_pixels_AVG, "POD7")

# deal with different lengths
pod7_dermal_pixel_thickness_prismDf<-create_dataframe(
      c(NA),    
      (filter_data_by_phrase(df2, p2))$average,
      (filter_data_by_phrase(df2, p3))$average,
      (filter_data_by_phrase(df2, p4))$average,
      (filter_data_by_phrase(df2, p5))$average)
colnames(pod7_dermal_pixel_thickness_prismDf) <- c("don't copy this column","No MAP", "L-MAP", "D-MAP", "R-MAP")
View(pod7_dermal_pixel_thickness_prismDf)
```

#### save the prism df's made in the previous chunk
```{r, save-prism-dfs}
# ONLY RUN IF THESE DF's AREN'T ALREADY SAVED!!
write.csv(pod4_epidermal_pixel_thickness_prismDf, file=paste0("../data/","pod4_epidermal_pixel_thickness_prismDf.csv"))
write.csv(pod4_dermal_pixel_thickness_prismDf, file=paste0("../data/","pod4_dermal_pixel_thickness_prismDf.csv"))

write.csv(pod7_epidermal_pixel_thickness_prismDf, file=paste0("../data/","pod7_epidermal_pixel_thickness_prismDf.csv"))
write.csv(pod7_dermal_pixel_thickness_prismDf, file=paste0("../data/","pod7_dermal_pixel_thickness_prismDf.csv"))
```

#### export to github for prism part 2
Run the following in terminal
git add ../data/pod4_epidermal_pixel_thickness_prismDf.csv 
git add ../data/pod4_dermal_pixel_thickness_prismDf.csv 
git add ../data/pod7_epidermal_pixel_thickness_prismDf.csv
git add ../data/pod7_dermal_pixel_thickness_prismDf.csv 
git commit -m "add prism part2 file"
git push

Then go to github and copy paste into excel
Then copy and past into prism