---
title: "050423-segura-meeting.Rmd"
output: html_document
date: "2023-04-05"
---

## 0a. load libraries
```{r, load}
library(tidyverse)
library(dplyr)

conversion = 100/22  #write multiplication conversion factor here; currently holds test value
```


## 0b. Read in the epidermis and dermis pixel dataframes 
skip first column (it is just the number of rows)
```{r, open-dermis-and-epidermis-dfs}
all_epidermis <- read_csv(paste0("../data/","all_epidermis_lengths_in_pixels.csv"))
a<-length(colnames(all_epidermis))

all_dermis <- read_csv(paste0("../data/","all_dermis_lengths_in_pixels.csv"))
b<-length(colnames(all_dermis))

# skip first column (it is just the number of rows)
all_epidermis <- all_epidermis[,2:a]
all_dermis <- all_dermis[,2:b]

# apply conversion
all_epidermis_micron <- all_epidermis/conversion
all_dermis_micron <- all_dermis/conversion
```

## 0c. Rename epidermis and dermis df for readability
```{r, load-pixel-epiderm-derm}

all_dermis_lengths_in_microns <- all_dermis_micron
all_epidermis_lengths_in_microns <- all_epidermis_micron
```

## Od. Generate density dataframes for each animal - DO NOT RE-RUN
```{r, interpolation}
# use interpolate to make dataframe with points that make outline of density plots
generate_density_data <- function(data) {
  num_columns <- ncol(data)
  
  # generate list for x and y values of 
  density_coordinates_list <- list()
  
  # make the list contain one dataframe for all the x values and one dataframe for all the y values
  density_coordinates_list$x <- vector()
  density_coordinates_list$y <- vector()
  
  # iterate over each column and generate a density plot for each 
  first_column <- data[,1]
  first_column <- first_column[!is.na(first_column)]
  first_density <- density(first_column)  
  
  maxX_length = length(first_density$x)
  maxY_length = length(first_density$y)
    
  for (i in 1:num_columns){
    this_column <- data[,i]
    #this_column <- data[,1]
    
    # remove missing values so R density() fnc can calculate densities
    this_column <- this_column[!is.na(this_column)]
    this_density <- density(this_column)
    
    thisX_length = length(this_density$x)
    thisY_length = length(this_density$y)
    
    # then add x values to dataframe in first list element, in the ith column
    # if(thisX_length>maxX_length){
    #   #add padding to vectors
    #   
    #   #and update max
    #   maxX_length = thisX_length
    # }
    density_coordinates_list$x <- cbind(density_coordinates_list$x, this_density$x)
    
    # then add y values to dataframe in second list element
    # if(thisY_length>maxY_length){
    #   #add padding to vectors
    #   #and update max
    #   maxY_length = thisX_length
    # }
    density_coordinates_list$y <- cbind(density_coordinates_list$y, this_density$y)
  } 
  
  # then name columns of dataframes stored in list
  density_coordinates_list$x <- data.frame(density_coordinates_list$x)
  density_coordinates_list$y <- data.frame(density_coordinates_list$y)
  
  colnames(density_coordinates_list$x) <- colnames(data)
  colnames(density_coordinates_list$y) <- colnames(data)
  
  # and return list
  return(density_coordinates_list)
}

# test_density <- generate_density_data(all_dermis_lengths_in_microns)
# (test_density$x)
# (test_density$y)

# test_dermis_density <- generate_density_data(all_dermis_lengths_in_microns)
# View(test_dermis_density$x)
# View(test_dermis_density$y)
all_dermis_densities<-generate_density_data(all_dermis_lengths_in_microns)


all_epidermis_densities<-generate_density_data(all_epidermis_lengths_in_microns)

# save densities as excel spreadsheets or csv files and export them
# then make excel spreadsheet where each df occupies one sheet
    # first Create a workbook object
    wb <- createWorkbook()
    
    # then add data frames to separate sheets
  addWorksheet(wb, sheetName = "density-x-coord")
  addWorksheet(wb, sheetName = "density-y-coord")
  
  writeData(wb,"density-x-coord",all_dermis_densities[[1]])
  writeData(wb,"density-y-coord",all_dermis_densities[[2]])
  
  # finally save the workbook to a file
saveWorkbook(wb, paste0("../data/230608-dermis-density-coordinates.xlsx"))

# do the same thing for epidermis data
    wb <- createWorkbook()
    
    # then add data frames to separate sheets
  addWorksheet(wb, sheetName = "density-x-coord")
  addWorksheet(wb, sheetName = "density-y-coord")
  
  writeData(wb,"density-x-coord",all_epidermis_densities[[1]])
  writeData(wb,"density-y-coord",all_epidermis_densities[[2]])
  
  # finally save the workbook to a file
saveWorkbook(wb, paste0("../data/230608-epidermis-density-coordinates.xlsx"))
```

##0e. also save density coordinates as csv files for ease of access with python pandas library DO NOT RE-RUN
```{r, generate-density-coord-csv}
# save x coord and y coord data frames as separate data frames for dermis
write.csv(all_dermis_densities[[1]],file="../data/230608-dermis-density-x-coordinates.csv")
write.csv(all_dermis_densities[[2]],file="../data/230608-dermis-density-y-coordinates.csv")

#...do the same for epidermis
write.csv(all_epidermis_densities[[1]],file="../data/230608-epidermis-density-x-coordinates.csv")
write.csv(all_epidermis_densities[[2]],file="../data/230608-epidermis-density-y-coordinates.csv")
```

## 1. import peak indices data
```{r, load-peak-indices}
epidermis_peak_indices <- read_csv("../data/230608-epidermis_peak_indices.csv")
dermis_peak_indices <- read_csv("../data/230608-dermis_peak_indices.csv")
```

## 1a. count the number of peaks for each animal/column
```{r, count-peaks}
epidermis_peak_counts <- data.frame(colSums(!is.na(epidermis_peak_indices)))
dermis_peak_counts <- data.frame(colSums(!is.na(dermis_peak_indices)))

colnames(epidermis_peak_counts) <- "number_of_peaks"
colnames(dermis_peak_counts) <- "number_of_peaks"

epidermis_peak_counts
dermis_peak_counts
```
## 2. write necessary funcitons

## 2a. write funciton to unblind animals
```{r, unblind-animals-fnc}
add_identity_unblind_column <- function(df) {
  # Define a lookup table of filename prefixes and corresponding identity_unblind values
  prefixes <- c("Animal_A.t" = "Exp17_Racemic-MAP_POD7_Mouse14",
                "Animal_C.t" = "Exp16_D-MAP_POD4_Mouse3",
                "Animal_D.t" = "Exp15_L-MAP_Mouse3_POD4",
                "Animal_F.t" = "Exp17_Racemic-MAP_POD7_Mouse11",
                "Animal_H.t" = "Exp17_Racemic-MAP_POD4_Mouse2",
                "Animal_I.t" = "Exp15_L-MAP_POD7_Mouse13",
                "Animal_J.t" = "Exp15_L-MAP_POD4_Mouse2",
                 "Animal_O.t" = "Exp17_Racemic-MAP_POD7_Mouse13",
                "Animal_W.t" = "Exp17_Racemic-MAP_POD7_Mouse12",
                "Animal_Y.t" = "Exp16_D-MAP_POD7_Mouse11",
                "Animal_Z1." = "Exp17_Racemic-MAP_POD4_Mouse1",
                "Animal_B.t" = "Exp15_POD7_Mouse11_L-MAP",
                "Animal_P.t" = "Exp14_POD7_Mouse13_D-MAP",
                "Animal_R.t" = "Exp16_POD7_Mouse2_D-MAP",
                "Animal_Z6." = "Exp16_POD7_Mouse11_D-MAP",
                "Animal_Z8." = "Exp16_POD4_Mouse2_D-MAP",
                 #"Animal_Z3." = "Exp15_Mouse12_POD7_LMAP",
                "Animal_Z9." = "Exp17_POD4_Mouse3_Racemic-MAP",
                "Animal_Z10" = "Exp16_POD4_Mouse1_D-MAP",
               
                "Animal_E.t" = "Exp14_No-MAP_POD7_Mouse11",
                "Animal_K.t" = "Exp14_No-MAP_POD4_Mouse4",
                "Animal_L.t" = "Exp14_No-MAP_POD7_Mouse12",
                "Animal_M.t" = "Exp14_No-MAP_POD4_Mouse3",
                "Animal_U.t" = "Exp14_No-MAP_POD4_Mouse1",
                "Animal_Z2." = "Exp14_POD7_Mouse14_No-MAP",
                "Animal_X.t" = "Exp14_No-MAP_POD4_Mouse2",
                
                "Animal_G.t" = "Unmanipulated_PepB",
                "Animal_N.t" = "Unmanip_PepB",
                "Animal_V.t" = "Unmanip_B6",
                "Animal_Z4." = "Exp15_POD4_Mouse1",
                "Animal_Z.t" = "UnmanipB6")
                
                
  
  # look up the identity_unblind value for each filename in the dataframe
  found<-vector(length=dim(df)[1])
  
  for(i in c(1:length(found))){
    this_fileName <- df[i,2]
    
    prefix <- substr(this_fileName, 1, 10) # Extract the first 10 characters of the filename
    this_label<-prefixes[prefix] # Look up the corresponding identity_unblind value
    found[i] <- this_label # and add label to vector
  }
  return(found)
}
```

## 2b. Write funciton to prepare unblinded data in excel for prism 
one excel document with two sheets
sheet1: epidermis treatments
sheet 2: dermis treatments
```{r, master-fnc-prism}
# load library for making excel spreadhseet
library(openxlsx)



# call all metric functions on data

# write helper function to group animals by one of three treatment groups (MAP, NoMAP, Unmanipulated)
mutate_map <- function(df){
  return(mutate(df,treatment = case_when(
  grepl("L-MAP|D-MAP|Racemic-MAP", identity_unblind) ~ "MAP",
  grepl("No-MAP", identity_unblind) ~ "NoMAP",
  grepl("Unmanip", identity_unblind) ~ "Unmanipulated",
  # assume unmanipulated if none of the above phrases are present
  !grepl("L-MAP|D-MAP|Racemic-MAP|No-MAP|Unmanip", identity_unblind) ~ "Unmanipulated",
  TRUE ~ NA_character_
)))
}

#Write helper function to filter data for prism
filter_data_by_phrase <- function(df, phrase) {
  filtered_df <- df[grep(phrase, df$treatment), ]
  return(filtered_df)
}

# set filtering phrases using ^ and $ to signify start and end of phrase for exact search/avoidign under-filtering 
p1<- "^Unmanipulated$"
p2<-"^NoMAP$"
p3<-"^MAP$"

# Wrtie helper fucntion to deal with different lengths for filtered data made for prism
create_dataframe <- function(vec1, vec2, vec3) {
  # Get the maximum length of the vectors
  max_length <- max(length(vec1), length(vec2), length(vec3))
  
  # Pad shorter vectors with NAs
  vec1 <- c(vec1, rep(NA, max_length - length(vec1)))
  vec2 <- c(vec2, rep(NA, max_length - length(vec2)))
  vec3 <- c(vec3, rep(NA, max_length - length(vec3)))

  # Create the data frame
  df <- data.frame(vec1, vec2, vec3)
  return(df)
}

master <- function(epidermis_data, dermis_data, col_idx_with_target_data, file_location){
   # then mutate so any map treatment is grouped
    data1_with_treatment_groups <- mutate_map(epidermis_data)
    data2_with_treatment_groups <- mutate_map(dermis_data)
  
  
  # and then make dataframe with a column each of the treatment groups (MAP, NoMAP, Unmanip)
    data1_sorted<-create_dataframe(
      (filter_data_by_phrase(data1_with_treatment_groups, p1))[,col_idx_with_target_data],
      (filter_data_by_phrase(data1_with_treatment_groups, p2))[,col_idx_with_target_data],
      (filter_data_by_phrase(data1_with_treatment_groups, p3))[,col_idx_with_target_data]
      )
    data2_sorted<-create_dataframe(
      (filter_data_by_phrase(data2_with_treatment_groups, p1))[,col_idx_with_target_data],
      (filter_data_by_phrase(data2_with_treatment_groups, p2))[,col_idx_with_target_data],
      (filter_data_by_phrase(data2_with_treatment_groups, p3))[,col_idx_with_target_data]
      )
    
    #... and change column names
    colnames(data1_sorted) <- c("Unmanipulated", "NoMAP", "MAP")
    colnames(data2_sorted) <- c("Unmanipulated", "NoMAP", "MAP")
  
    
    # View(data1_sorted)
    # View(data2_sorted)
    
    # then make excel spreadsheet where each df occupies one sheet
    # first Create a workbook object
    wb <- createWorkbook()
    
    # then add data frames to separate sheets
  addWorksheet(wb, sheetName = "epidermis")
  addWorksheet(wb, sheetName = "dermis")
  
  writeData(wb,"epidermis",data1_sorted)
  writeData(wb,"dermis",data2_sorted)
  
  # finally save the workbook to a file
saveWorkbook(wb, file_location)
}
```

## 3a. unblind animal peak counts
```{r, unblind-peak-counts}
# add column that is the animal name
dermis_peak_counts$filename <- colnames(dermis_peak_indices)
epidermis_peak_counts$filename <- colnames(epidermis_peak_indices)

# then add unblind column
dermis_peak_counts$identity_unblind <- add_identity_unblind_column(dermis_peak_counts)
epidermis_peak_counts$identity_unblind <- add_identity_unblind_column(epidermis_peak_counts)
```

## 3b. then prepare peak count data for prism (by making excel spreadsheets)
```{r, peak-count-prism-data}
master(epidermis_peak_counts, dermis_peak_counts, 1, "../data/230608-prism-peak-counts-output.xlsx")
```

## 4. Calculate integral for one animal using rectangle method
## 4a. First use ggplot to make histograms for all data and confirm binwidth=2 is suitable baseline

```{r, dertermine-bindwidth-for-lengths}
# comment out accordign to if want to vizualize dermis or epidermis
# df_set1<-all_dermis_lengths_in_microns[,1:6]
# df_set2<-all_dermis_lengths_in_microns[,7:12]
# df_set3<-all_dermis_lengths_in_microns[,13:18]
# df_set4<-all_dermis_lengths_in_microns[,19:24]
# df_set5<-all_dermis_lengths_in_microns[,25:30]

df_set1<-all_epidermis_lengths_in_microns[,1:6]
df_set2<-all_epidermis_lengths_in_microns[,7:12]
df_set3<-all_epidermis_lengths_in_microns[,13:18]
df_set4<-all_epidermis_lengths_in_microns[,19:24]
df_set5<-all_epidermis_lengths_in_microns[,25:30]
# set y-axis range
x_range <- c(0,275)

# convert data to long format using tidyr::pivot_longer()
long1 <- tidyr::pivot_longer(df_set1, everything())
long2 <- tidyr::pivot_longer(df_set2, everything())
long3 <- tidyr::pivot_longer(df_set3, everything())
long4 <- tidyr::pivot_longer(df_set4, everything())
long5 <- tidyr::pivot_longer(df_set5, everything())
# set y-axis range
x_range <- c(0,150)

# plot using ggplot and facet_wrap()
ggplot(long1[], aes(x = value)) +
  geom_histogram(color="black", fill="white", binwidth = 2) +
  facet_wrap(~ name, scales = "fixed") +
  labs(x = "Micron Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text())

ggplot(long2[], aes(x = value)) +
  geom_histogram(color="black", fill="white", binwidth = 2) +
  facet_wrap(~ name, scales = "fixed") +
  labs(x = "Micron Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text())

ggplot(long3[], aes(x = value)) +
  geom_histogram(color="black", fill="white", binwidth = 2) +
  facet_wrap(~ name, scales = "fixed") +
  labs(x = "Micron Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text())

ggplot(long4[], aes(x = value)) +
  geom_histogram(color="black", fill="white", binwidth = 2) +
  facet_wrap(~ name, scales = "fixed") +
  labs(x = "Micron Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text())

ggplot(long5[], aes(x = value)) +
  geom_histogram(color="black", fill="white", binwidth = 2) +
  facet_wrap(~ name, scales = "fixed") +
  labs(x = "Micron Value", y = "Frequency")+
  scale_x_continuous(limits = x_range, expand = c(0, 0))+
  theme(axis.title.x = element_text()) 
```

##4b. then write funciton to calculate integral taking into account "optimal" binwidth (of 2)
```{r, get-hist-bin-counts}
rectangle_integral <- function(df, binwidth = 2) {
  integral_values <- vector()
  
  for (i in 1:ncol(df)) {
    values <- df[,i]
    #remove missign values
    values<-values[!is.na(values)]
    
    # Create the histogram plot
    hist_plot <- ggplot(data.frame(values), aes(x = values)) +
      geom_histogram(binwidth = binwidth)
    
    # Build the plot
    built_plot <- ggplot_build(hist_plot)
    
    # Extract the counts from the plot data
    counts <- built_plot$data[[1]]$count
    
    # Calculate the integral by multiplying every number in the count vector by binwidth
    integral <- sum(binwidth * counts)
    
    integral_values[i] <- integral
  }
  
  # Return integral values
  return(integral_values)
}

dermis_integral_approx<-rectangle_integral(all_dermis_lengths_in_microns)
epidermis_integral_approx<-rectangle_integral(all_epidermis_lengths_in_microns)

```

##4c. label integral values and prepare for prism
```{r, prepare itnegral-data-for-prism}
# make integral dataframe by matching with animal
dermis_integral_approx_df<-data.frame(dermis_integral_approx, colnames(all_dermis_lengths_in_microns))
colnames(dermis_integral_approx_df) <- c("integral", "filename")

epidermis_integral_approx_df<-data.frame(epidermis_integral_approx, colnames(all_epidermis_lengths_in_microns))
colnames(epidermis_integral_approx_df) <- c("integral", "filename")

# unblind
dermis_integral_approx_df$identity_unblind <- add_identity_unblind_column(dermis_integral_approx_df)
epidermis_integral_approx_df$identity_unblind <- add_identity_unblind_column(epidermis_integral_approx_df)

# prepare for prism
master(epidermis_integral_approx_df, dermis_integral_approx_df, 1, "../data/230608-prism-integration-output.xlsx")
```


