---
title: "050423-segura-meeting.Rmd"
output: html_document
date: "2023-04-05"
---

## 0a. load libraries
```{r, load}
library(tidyverse)
library(dplyr)

conversion = 100/22  #write multiplication conversion factor here; currently holds test value
```


## 0b. Read in the epidermis and dermis pixel dataframes 
skip first column (it is just the number of rows)
```{r, open-dermis-and-epidermis-dfs}
all_epidermis <- read_csv(paste0("../data/","all_epidermis_lengths_in_pixels.csv"))
a<-length(colnames(all_epidermis))

all_dermis <- read_csv(paste0("../data/","all_dermis_lengths_in_pixels.csv"))
b<-length(colnames(all_dermis))

# skip first column (it is just the number of rows)
all_epidermis <- all_epidermis[,2:a]
all_dermis <- all_dermis[,2:b]

# apply conversion
all_epidermis_micron <- all_epidermis/conversion
all_dermis_micron <- all_dermis/conversion
```

## 0c. Rename epidermis and dermis df for readability
```{r, load-pixel-epiderm-derm}

all_dermis_lengths_in_microns <- all_dermis_micron
all_epidermis_lengths_in_microns <- all_epidermis_micron
```

## Od. Generate density dataframes for each animal - DO NOT RE-RUN
```{r, interpolation}
# use interpolate to make dataframe with points that make outline of density plots
generate_density_data <- function(data) {
  num_columns <- ncol(data)
  
  # generate list for x and y values of 
  density_coordinates_list <- list()
  
  # make the list contain one dataframe for all the x values and one dataframe for all the y values
  density_coordinates_list$x <- vector()
  density_coordinates_list$y <- vector()
  
  # iterate over each column and generate a density plot for each 
  first_column <- data[,1]
  first_column <- first_column[!is.na(first_column)]
  first_density <- density(first_column)  
  
  maxX_length = length(first_density$x)
  maxY_length = length(first_density$y)
    
  for (i in 1:num_columns){
    this_column <- data[,i]
    #this_column <- data[,1]
    
    # remove missing values so R density() fnc can calculate densities
    this_column <- this_column[!is.na(this_column)]
    this_density <- density(this_column)
    
    thisX_length = length(this_density$x)
    thisY_length = length(this_density$y)
    
    # then add x values to dataframe in first list element, in the ith column
    # if(thisX_length>maxX_length){
    #   #add padding to vectors
    #   
    #   #and update max
    #   maxX_length = thisX_length
    # }
    density_coordinates_list$x <- cbind(density_coordinates_list$x, this_density$x)
    
    # then add y values to dataframe in second list element
    # if(thisY_length>maxY_length){
    #   #add padding to vectors
    #   #and update max
    #   maxY_length = thisX_length
    # }
    density_coordinates_list$y <- cbind(density_coordinates_list$y, this_density$y)
  } 
  
  # then name columns of dataframes stored in list
  density_coordinates_list$x <- data.frame(density_coordinates_list$x)
  density_coordinates_list$y <- data.frame(density_coordinates_list$y)
  
  colnames(density_coordinates_list$x) <- colnames(data)
  colnames(density_coordinates_list$y) <- colnames(data)
  
  # and return list
  return(density_coordinates_list)
}

# test_density <- generate_density_data(all_dermis_lengths_in_microns)
# (test_density$x)
# (test_density$y)

# test_dermis_density <- generate_density_data(all_dermis_lengths_in_microns)
# View(test_dermis_density$x)
# View(test_dermis_density$y)
all_dermis_densities<-generate_density_data(all_dermis_lengths_in_microns)


all_epidermis_densities<-generate_density_data(all_epidermis_lengths_in_microns)

# save densities as excel spreadsheets or csv files and export them
# then make excel spreadsheet where each df occupies one sheet
    # first Create a workbook object
    wb <- createWorkbook()
    
    # then add data frames to separate sheets
  addWorksheet(wb, sheetName = "density-x-coord")
  addWorksheet(wb, sheetName = "density-y-coord")
  
  writeData(wb,"density-x-coord",all_dermis_densities[[1]])
  writeData(wb,"density-y-coord",all_dermis_densities[[2]])
  
  # finally save the workbook to a file
saveWorkbook(wb, paste0("../data/230608-dermis-density-coordinates.xlsx"))

# do the same thing for epidermis data
    wb <- createWorkbook()
    
    # then add data frames to separate sheets
  addWorksheet(wb, sheetName = "density-x-coord")
  addWorksheet(wb, sheetName = "density-y-coord")
  
  writeData(wb,"density-x-coord",all_epidermis_densities[[1]])
  writeData(wb,"density-y-coord",all_epidermis_densities[[2]])
  
  # finally save the workbook to a file
saveWorkbook(wb, paste0("../data/230608-epidermis-density-coordinates.xlsx"))
```

##0e. also save density coordinates as csv files for ease of access with python pandas library DO NOT RE-RUN
```{r, generate-density-coord-csv}
# save x coord and y coord data frames as separate data frames for dermis
write.csv(all_dermis_densities[[1]],file="../data/230608-dermis-density-x-coordinates.csv")
write.csv(all_dermis_densities[[2]],file="../data/230608-dermis-density-y-coordinates.csv")

#...do the same for epidermis
write.csv(all_epidermis_densities[[1]],file="../data/230608-epidermis-density-x-coordinates.csv")
write.csv(all_epidermis_densities[[2]],file="../data/230608-epidermis-density-y-coordinates.csv")
```

## 1. import peak indices data
```{r, load-peak-indices}
epidermis_peak_indices <- read_csv("../data/230608-epidermis_peak_indices.csv")
dermis_peak_indices <- read_csv("../data/230608-dermis_peak_indices.csv")
```

## 1a. count the number of peaks for each animal/column
```{r, count-peaks}
epidermis_peak_counts <- data.frame(colSums(!is.na(epidermis_peak_indices)))
dermis_peak_counts <- data.frame(colSums(!is.na(dermis_peak_indices)))

colnames(epidermis_peak_counts) <- "number_of_peaks"
colnames(dermis_peak_counts) <- "number_of_peaks"

epidermis_peak_counts
dermis_peak_counts
```
## 2. write necessary funcitons

## 2a. write funciton to unblind animals
```{r, unblind-animals-fnc}
add_identity_unblind_column <- function(df) {
  # Define a lookup table of filename prefixes and corresponding identity_unblind values
  prefixes <- c("Animal_A.t" = "Exp17_Racemic-MAP_POD7_Mouse14",
                "Animal_C.t" = "Exp16_D-MAP_POD4_Mouse3",
                "Animal_D.t" = "Exp15_L-MAP_Mouse3_POD4",
                "Animal_F.t" = "Exp17_Racemic-MAP_POD7_Mouse11",
                "Animal_H.t" = "Exp17_Racemic-MAP_POD4_Mouse2",
                "Animal_I.t" = "Exp15_L-MAP_POD7_Mouse13",
                "Animal_J.t" = "Exp15_L-MAP_POD4_Mouse2",
                 "Animal_O.t" = "Exp17_Racemic-MAP_POD7_Mouse13",
                "Animal_W.t" = "Exp17_Racemic-MAP_POD7_Mouse12",
                "Animal_Y.t" = "Exp16_D-MAP_POD7_Mouse11",
                "Animal_Z1." = "Exp17_Racemic-MAP_POD4_Mouse1",
                "Animal_B.t" = "Exp15_POD7_Mouse11_L-MAP",
                "Animal_P.t" = "Exp14_POD7_Mouse13_D-MAP",
                "Animal_R.t" = "Exp16_POD7_Mouse2_D-MAP",
                "Animal_Z6." = "Exp16_POD7_Mouse11_D-MAP",
                "Animal_Z8." = "Exp16_POD4_Mouse2_D-MAP",
                 #"Animal_Z3." = "Exp15_Mouse12_POD7_LMAP",
                "Animal_Z9." = "Exp17_POD4_Mouse3_Racemic-MAP",
                "Animal_Z10" = "Exp16_POD4_Mouse1_D-MAP",
               
                "Animal_E.t" = "Exp14_No-MAP_POD7_Mouse11",
                "Animal_K.t" = "Exp14_No-MAP_POD4_Mouse4",
                "Animal_L.t" = "Exp14_No-MAP_POD7_Mouse12",
                "Animal_M.t" = "Exp14_No-MAP_POD4_Mouse3",
                "Animal_U.t" = "Exp14_No-MAP_POD4_Mouse1",
                "Animal_Z2." = "Exp14_POD7_Mouse14_No-MAP",
                "Animal_X.t" = "Exp14_No-MAP_POD4_Mouse2",
                
                "Animal_G.t" = "Unmanipulated_PepB",
                "Animal_N.t" = "Unmanip_PepB",
                "Animal_V.t" = "Unmanip_B6",
                "Animal_Z4." = "Exp15_POD4_Mouse1",
                "Animal_Z.t" = "UnmanipB6")
                
                
  
  # look up the identity_unblind value for each filename in the dataframe
  found<-vector(length=dim(df)[1])
  
  for(i in c(1:length(found))){
    this_fileName <- df[i,2]
    
    prefix <- substr(this_fileName, 1, 10) # Extract the first 10 characters of the filename
    this_label<-prefixes[prefix] # Look up the corresponding identity_unblind value
    found[i] <- this_label # and add label to vector
  }
  return(found)
}
```

## 2b. Write funciton to prepare unblinded data in excel for prism 
one excel document with two sheets
sheet1: epidermis treatments
sheet 2: dermis treatments
```{r, master-fnc-prism}
# load library for making excel spreadhseet
library(openxlsx)



# call all metric functions on data

# write helper function to group animals by one of three treatment groups (MAP, NoMAP, Unmanipulated)
mutate_map <- function(df){
  return(mutate(df,treatment = case_when(
  grepl("L-MAP|D-MAP|Racemic-MAP", identity_unblind) ~ "MAP",
  grepl("No-MAP", identity_unblind) ~ "NoMAP",
  grepl("Unmanip", identity_unblind) ~ "Unmanipulated",
  # assume unmanipulated if none of the above phrases are present
  !grepl("L-MAP|D-MAP|Racemic-MAP|No-MAP|Unmanip", identity_unblind) ~ "Unmanipulated",
  TRUE ~ NA_character_
)))
}

#Write helper function to filter data for prism
filter_data_by_phrase <- function(df, phrase) {
  filtered_df <- df[grep(phrase, df$treatment), ]
  return(filtered_df)
}

# set filtering phrases using ^ and $ to signify start and end of phrase for exact search/avoidign under-filtering 
p1<- "^Unmanipulated$"
p2<-"^NoMAP$"
p3<-"^MAP$"

# Wrtie helper fucntion to deal with different lengths for filtered data made for prism
create_dataframe <- function(vec1, vec2, vec3) {
  # Get the maximum length of the vectors
  max_length <- max(length(vec1), length(vec2), length(vec3))
  
  # Pad shorter vectors with NAs
  vec1 <- c(vec1, rep(NA, max_length - length(vec1)))
  vec2 <- c(vec2, rep(NA, max_length - length(vec2)))
  vec3 <- c(vec3, rep(NA, max_length - length(vec3)))

  # Create the data frame
  df <- data.frame(vec1, vec2, vec3)
  return(df)
}

master <- function(epidermis_data, dermis_data, col_idx_with_target_data, file_location){
   # then mutate so any map treatment is grouped
    data1_with_treatment_groups <- mutate_map(epidermis_data)
    data2_with_treatment_groups <- mutate_map(dermis_data)
  
  
  # and then make dataframe with a column each of the treatment groups (MAP, NoMAP, Unmanip)
    data1_sorted<-create_dataframe(
      (filter_data_by_phrase(data1_with_treatment_groups, p1))[,col_idx_with_target_data],
      (filter_data_by_phrase(data1_with_treatment_groups, p2))[,col_idx_with_target_data],
      (filter_data_by_phrase(data1_with_treatment_groups, p3))[,col_idx_with_target_data]
      )
    data2_sorted<-create_dataframe(
      (filter_data_by_phrase(data2_with_treatment_groups, p1))[,col_idx_with_target_data],
      (filter_data_by_phrase(data2_with_treatment_groups, p2))[,col_idx_with_target_data],
      (filter_data_by_phrase(data2_with_treatment_groups, p3))[,col_idx_with_target_data]
      )
    
    #... and change column names
    colnames(data1_sorted) <- c("Unmanipulated", "NoMAP", "MAP")
    colnames(data2_sorted) <- c("Unmanipulated", "NoMAP", "MAP")
  
    
    # View(data1_sorted)
    # View(data2_sorted)
    
    # then make excel spreadsheet where each df occupies one sheet
    # first Create a workbook object
    wb <- createWorkbook()
    
    # then add data frames to separate sheets
  addWorksheet(wb, sheetName = "epidermis")
  addWorksheet(wb, sheetName = "dermis")
  
  writeData(wb,"epidermis",data1_sorted)
  writeData(wb,"dermis",data2_sorted)
  
  # finally save the workbook to a file
saveWorkbook(wb, file_location)
}
```

## 3a. unblind animal peak counts
```{r, unblind-peak-counts}
# add column that is the animal name
dermis_peak_counts$filename <- colnames(dermis_peak_indices)
epidermis_peak_counts$filename <- colnames(epidermis_peak_indices)

# then add unblind column
dermis_peak_counts$identity_unblind <- add_identity_unblind_column(dermis_peak_counts)
epidermis_peak_counts$identity_unblind <- add_identity_unblind_column(epidermis_peak_counts)
```

## 3b. then prepare peak count data for prism (by making excel spreadsheets)
```{r, peak-count-prism-data}
master(epidermis_peak_counts, dermis_peak_counts, 1, "../data/230608-prism-peak-counts-output.xlsx")
```

## 1. write function to calculate integral of density plots
```{r, fnc-integral}
# this function takes a data frame 'data' where each column corresponds to a specific histology section and each row contains epidermis or dermis lengths in microns for a particular histology section. For example:

# Animal_A | Animal_B | Animal_C | . . .
# ---------|----------|----------| -----
#   53.9   |   2.20   |   22.0   | 
#   53.68  |   2.24   |  21.78.  | . . .
#   . . .  |  . . .   |  . . .   |


calculate_auc <- function(data) {
  library(stats)
  
  num_columns <- ncol(data)
   #initializes an empty vector to store the area under the curve values for each column.
  auc_results <- vector("numeric", length = num_columns)
  
  for (i in 1:num_columns){
  # iterate over each column and generate a density plot for each 

    this_column <- data[,i]
    
    # remove missing values so R density() fnc can calculate densities
    this_column <- this_column[!is.na(this_column)]
    this_density <- density(this_column)
    
    # calculate area under curve with definite integral
    # 1. define a function using interpolation that describes the density curve for the integrate() R function to use
      this_densityEquation <- approxfun(this_density$x,this_density$y)
    # 2. then call integrate() function
    auc <- integrate(this_densityEquation, lower=min(this_column), upper=max(this_column),subdivisions = 2000)$value
    # and save to vector
    auc_results[i] <- auc
    
  }
  return(auc_results)
}
```

## 1b. take 2 at integral function
```{r,diff-fnc}
library(pracma)

calculate_auc <- function(data) {
  library(stats)
  
  num_columns <- ncol(data)
   #initializes an empty vector to store the area under the curve values for each column.
  auc_results <- vector("numeric", length = num_columns)
  
  for (i in 1:num_columns){
  # iterate over each column and generate a density plot for each 

    this_column <- data[,i]
    
    # remove missing values so R density() fnc can calculate densities
    this_column <- this_column[!is.na(this_column)]
    this_density <- density(this_column)
    
    # calculate area under curve with definite integral
    # 1. define a function using interpolation that describes the density curve for the integrate() R function to use
      this_densityEquation <- approxfun(this_density$x,this_density$y)
      
      # Define the Simpson's rule integration function
simpsons_integration <- function(f, lower, upper, n = 1000) {
  x <- seq(lower, upper, length.out = n + 1)
  h <- (upper - lower) / n
  y <- f(x)
  
  even_sum <- sum(y[seq(2, n, 2)])
  odd_sum <- sum(y[seq(3, n-1, 2)])
  
  integral <- (h/3) * (y[1] + y[n+1] + 4 * odd_sum + 2 * even_sum)
  return(integral)
}

# Calculate the integral of the function using Simpson's rule
integral_result <- simpsons_integration(this_densityEquation, lower = 0, upper = 1)
      
      #auc <- integrate.quad(this_densityEquation, min(this_column), max(this_column))$value
      
    auc_results[i] <- integral_result
    
  }
  return(auc_results)
}
```
## 2a. test density function approxfun() to make sure it makes a density plot similar to actual
```{r, test-approxfun}
test_data<-(all_epidermis_lengths_in_microns[,1])[!is.na(all_epidermis_lengths_in_microns[,1])]
x<-density(test_data)$x
y<-density(test_data)$y
this_densityEquation <- approxfun(x,y)


# actual plot
df_set1<-all_epidermis_lengths_in_microns[,1:6]
long1 <- tidyr::pivot_longer(df_set1, everything())
targetAnimal_only <- long1[] %>% filter(startsWith(name, "Animal_A."))

actual_densityplot<-ggplot(targetAnimal_only, aes(x = value)) +
  geom_density(fill = "grey", color="transparent", alpha = 0.5) +
  theme_minimal()+
  labs(x = "Micron Value", y = "Frequency")+
  scale_x_continuous(limits = c(0,80), expand = c(0, 0))+
  theme(axis.title.x = element_text())

curve(this_densityEquation, from = 0, to = 80, n = 1000, xlab = "x", ylab = "y", main = "Outline of the Function")
actual_densityplot

# check that my function calculated integral correctly
(integrate(this_densityEquation, min(test_data), max(test_data))$value) == calculate_auc(all_epidermis_lengths_in_microns)[1]
```
## 2b. Continued testing of function
```{r, testing-cont}
#standard numeric
data <- data.frame(
  col1 = c(1, 2, 3, 4, 5),
  col2 = c(6, 7, 8, 9, 10),
  col3 = c(11, 12, 13, 14, 15)
)

result <- calculate_auc(data)
print(result)
# expected 1.683505 1.683505 1.683505

# negative values
data <- data.frame(
  col1 = c(-1, -2, -3, -4, -5),
  col2 = c(-6, -7, -8, -9, -10),
  col3 = c(-11, -12, -13, -14, -15)
)

result <- calculate_auc(data)
print(result)
# expected 1.683505 1.683505 1.683505

# missing values
data <- data.frame(
  col1 = c(1, 2, NA, 4, 5),
  col2 = c(6, NA, 8, 9, 10),
  col3 = c(11, 12, 13, NA, 15)
)

result <- calculate_auc(data)
print(result)
# expected [1] 1.683505 1.683505 1.683505

# different density curves
set.seed(123)
data <- data.frame(
  col1 = rnorm(100),
  col2 = rnorm(100, mean = 2),
  col3 = rnorm(100, mean = -2)
)

result <- calculate_auc(data)
print(result)
# expected  0.3318891 0.3077189 0.3318891
```

## 3. Calculate the area under the curve of ach animal's density plots for epidermis and dermis
```{r, calc-integral}
epidermis_auc <- calculate_auc(all_epidermis_lengths_in_microns)
dermis_auc <- calculate_auc(all_dermis_lengths_in_microns)
```

## 4. Label integrals with animal and treatment
### 4a. Write funciton to unblind animal identities found in auc df's
```{r, unblind-fnc}
add_identity_unblind_column <- function(df) {
  # Define a lookup table of filename prefixes and corresponding identity_unblind values
  prefixes <- c("Animal_A.t" = "Exp17_Racemic-MAP_POD7_Mouse14",
                "Animal_C.t" = "Exp16_D-MAP_POD4_Mouse3",
                "Animal_D.t" = "Exp15_L-MAP_Mouse3_POD4",
                "Animal_F.t" = "Exp17_Racemic-MAP_POD7_Mouse11",
                "Animal_H.t" = "Exp17_Racemic-MAP_POD4_Mouse2",
                "Animal_I.t" = "Exp15_L-MAP_POD7_Mouse13",
                "Animal_J.t" = "Exp15_L-MAP_POD4_Mouse2",
                 "Animal_O.t" = "Exp17_Racemic-MAP_POD7_Mouse13",
                "Animal_W.t" = "Exp17_Racemic-MAP_POD7_Mouse12",
                "Animal_Y.t" = "Exp16_D-MAP_POD7_Mouse11",
                "Animal_Z1." = "Exp17_Racemic-MAP_POD4_Mouse1",
                "Animal_B.t" = "Exp15_POD7_Mouse11_L-MAP",
                "Animal_P.t" = "Exp14_POD7_Mouse13_D-MAP",
                "Animal_R.t" = "Exp16_POD7_Mouse2_D-MAP",
                "Animal_Z6." = "Exp16_POD7_Mouse11_D-MAP",
                "Animal_Z8." = "Exp16_POD4_Mouse2_D-MAP",
                 #"Animal_Z3." = "Exp15_Mouse12_POD7_LMAP",
                "Animal_Z9." = "Exp17_POD4_Mouse3_Racemic-MAP",
                "Animal_Z10" = "Exp16_POD4_Mouse1_D-MAP",
               
                "Animal_E.t" = "Exp14_No-MAP_POD7_Mouse11",
                "Animal_K.t" = "Exp14_No-MAP_POD4_Mouse4",
                "Animal_L.t" = "Exp14_No-MAP_POD7_Mouse12",
                "Animal_M.t" = "Exp14_No-MAP_POD4_Mouse3",
                "Animal_U.t" = "Exp14_No-MAP_POD4_Mouse1",
                "Animal_Z2." = "Exp14_POD7_Mouse14_No-MAP",
                "Animal_X.t" = "Exp14_No-MAP_POD4_Mouse2",
                
                "Animal_G.t" = "Unmanipulated_PepB",
                "Animal_N.t" = "Unmanip_PepB",
                "Animal_V.t" = "Unmanip_B6",
                "Animal_Z4." = "Exp15_POD4_Mouse1",
                "Animal_Z.t" = "UnmanipB6")
                
                
  
  # look up the identity_unblind value for each filename in the dataframe
  found<-vector(length=dim(df)[1])
  
  for(i in c(1:length(found))){
    this_fileName <- df[i,2]
    
    prefix <- substr(this_fileName, 1, 10) # Extract the first 10 characters of the filename
    this_label<-prefixes[prefix] # Look up the corresponding identity_unblind value
    found[i] <- this_label # and add label to vector
  }
  return(found)
}

```

### 4b. make integral dataframe with animal names and treatment groups 
```{r, label-integrals}
# make integral dataframes
labelled_epidermis_auc <- data.frame(epidermis_auc, colnames(all_epidermis_lengths_in_microns))
labelled_dermis_auc <- data.frame(dermis_auc, colnames(all_dermis_lengths_in_microns))

# label columns
colnames(labelled_dermis_auc) <- c("auc", "animal")
colnames(labelled_epidermis_auc) <- c("auc", "animal")

labelled_dermis_auc$identity_unblind <- add_identity_unblind_column(labelled_dermis_auc)
labelled_epidermis_auc$identity_unblind <- add_identity_unblind_column(labelled_epidermis_auc)
```

## 4. Write function to turn integral df's into excel spreadsheet
one excel document with two sheets
sheet1: epidermis treatments
sheet 2: dermis treatments
```{r, master-fnc-prism}
# load library for making excel spreadhseet
library(openxlsx)



# call all metric functions on data

# write helper function to group animals by one of three treatment groups (MAP, NoMAP, Unmanipulated)
mutate_map <- function(df){
  return(mutate(df,treatment = case_when(
  grepl("L-MAP|D-MAP|Racemic-MAP", identity_unblind) ~ "MAP",
  grepl("No-MAP", identity_unblind) ~ "NoMAP",
  grepl("Unmanip", identity_unblind) ~ "Unmanipulated",
  # assume unmanipulated if none of the above phrases are present
  !grepl("L-MAP|D-MAP|Racemic-MAP|No-MAP|Unmanip", identity_unblind) ~ "Unmanipulated",
  TRUE ~ NA_character_
)))
}

#Write helper function to filter data for prism
filter_data_by_phrase <- function(df, phrase) {
  filtered_df <- df[grep(phrase, df$treatment), ]
  return(filtered_df)
}

# set filtering phrases using ^ and $ to signify start and end of phrase for exact search/avoidign under-filtering 
p1<- "^Unmanipulated$"
p2<-"^NoMAP$"
p3<-"^MAP$"

# Wrtie helper fucntion to deal with different lengths for filtered data made for prism
create_dataframe <- function(vec1, vec2, vec3) {
  # Get the maximum length of the vectors
  max_length <- max(length(vec1), length(vec2), length(vec3))
  
  # Pad shorter vectors with NAs
  vec1 <- c(vec1, rep(NA, max_length - length(vec1)))
  vec2 <- c(vec2, rep(NA, max_length - length(vec2)))
  vec3 <- c(vec3, rep(NA, max_length - length(vec3)))

  # Create the data frame
  df <- data.frame(vec1, vec2, vec3)
  return(df)
}

master <- function(epidermis_data, dermis_data){
   # then mutate so any map treatment is grouped
    data1_with_treatment_groups <- mutate_map(epidermis_data)
    data2_with_treatment_groups <- mutate_map(dermis_data)
  
  
  # and then make dataframe with a column each of the treatment groups (MAP, NoMAP, Unmanip)
    data1_sorted<-create_dataframe(
      (filter_data_by_phrase(data1_with_treatment_groups, p1))$auc,
      (filter_data_by_phrase(data1_with_treatment_groups, p2))$auc,
      (filter_data_by_phrase(data1_with_treatment_groups, p3))$auc
      )
    data2_sorted<-create_dataframe(
      (filter_data_by_phrase(data2_with_treatment_groups, p1))$auc,
      (filter_data_by_phrase(data2_with_treatment_groups, p2))$auc,
      (filter_data_by_phrase(data2_with_treatment_groups, p3))$auc
      )
    
    #... and change column names
    colnames(data1_sorted) <- c("Unmanipulated", "NoMAP", "MAP")
    colnames(data2_sorted) <- c("Unmanipulated", "NoMAP", "MAP")
  
    
    # then make excel spreadsheet where each df occupies one sheet
    # first Create a workbook object
    wb <- createWorkbook()
    
    # then add data frames to separate sheets
  addWorksheet(wb, sheetName = "epidermis")
  addWorksheet(wb, sheetName = "dermis")
  
  writeData(wb,"epidermis",data1_sorted)
  writeData(wb,"dermis",data2_sorted)
  
  # finally save the workbook to a file
saveWorkbook(wb, paste0("../data/230523-prism-integrals-output.xlsx"))
}
```


## 5a. Use function to turn integral df's into excel spreadsheet
```{r, use-master-fnc}
master(labelled_epidermis_auc, labelled_dermis_auc)
```


## 6. save epidermis and dermis micron length csv files for python access
```{r, make-micron-csv}
write.csv(all_epidermis_lengths_in_microns, file="../data/all_epidermis_lengths_in_microns.csv")
write.csv(all_dermis_lengths_in_microns, file="../data/all_dermis_lengths_in_microns.csv")
```

