---
title: "Code-Along"
output: html_document
date: "2023-03-30"
---

THE FOLLOWING SPECIFICALLY LOOKS AT MICRON PIXEL CONVERSION AFTER ...segura-meeting.Rmd has been run
### load libraries
```{r, load}
library(tidyverse)
library(dplyr)

conversion = 100/22  #write multiplication conversion factor here; currently holds test value
```

### Read in the epidermis and dermis pixel dataframes 
skip first column (it is just the number of rows)
```{r, open-dermis-and-epidermis-dfs}
all_epidermis <- read_csv(paste0("../data/","all_epidermis_lengths_in_pixels.csv"))
a<-length(colnames(all_epidermis))

all_dermis <- read_csv(paste0("../data/","all_dermis_lengths_in_pixels.csv"))
b<-length(colnames(all_dermis))

# skip first column (it is just the number of rows)
all_epidermis <- all_epidermis[,2:a]
all_dermis <- all_dermis[,2:b]

# apply conversion
all_epidermis_micron <- all_epidermis*conversion
all_dermis_micron <- all_dermis*conversion
```

### rename epidermis and dermis df for readability
```{r, load-pixel-epiderm-derm}
all_dermis_lengths_in_microns <- all_dermis
all_epidermis_lengths_in_microns <- all_epidermis
```

### visualize spread of each animal's micrin lengths...
#### spread of each animal's micron lengths for epidermis
```{r, spread-epi-pixel}
df_set1<-all_epidermis_lengths_in_microns[,1:6]
df_set2<-all_epidermis_lengths_in_microns[,7:12]
df_set3<-all_epidermis_lengths_in_microns[,13:18]
df_set4<-all_epidermis_lengths_in_microns[,19:24]
df_set5<-all_epidermis_lengths_in_microns[,25:length(all_epidermis_lengths_in_microns)]

# convert data to long format using tidyr::pivot_longer()
long1 <- tidyr::pivot_longer(df_set1, everything())
long2 <- tidyr::pivot_longer(df_set2, everything())
long3 <- tidyr::pivot_longer(df_set3, everything())
long4 <- tidyr::pivot_longer(df_set4, everything())
long5 <- tidyr::pivot_longer(df_set5, everything())

# plot using ggplot and facet_wrap()
p1<-ggplot(long1[], aes(x = value)) +
  geom_histogram(color="black", fill="white") +
  facet_wrap(~ name, scales = "free") +
  labs(x = "Micron Value", y = "Frequency")
p1
#ggsave("animal-micron-length-spread1.jpg", plot = p1, dpi = 300, width = 6, height = 4, units = "in")

p2<-ggplot(long2[], aes(x = value)) +
  geom_histogram(color="black", fill="white") +
  facet_wrap(~ name, scales = "free") +
  labs(x = "Micron Value", y = "Frequency")
p2
#ggsave("animal-micron-length-spread2.jpg", plot = p2, dpi = 300, width = 6, height = 4, units = "in")

p3<-ggplot(long3[], aes(x = value)) +
  geom_histogram(color="black", fill="white") +
  facet_wrap(~ name, scales = "free") +
  labs(x = "Micron Value", y = "Frequency")
#ggsave("animal-micron-length-spread3.jpg", plot = p3, dpi = 300, width = 6, height = 4, units = "in")

p4<-ggplot(long4[], aes(x = value)) +
  geom_histogram(color="black", fill="white") +
  facet_wrap(~ name, scales = "free") +
  labs(x = "Micron Value", y = "Frequency")
#ggsave("animal-micron-length-spread4.jpg", plot = p4, dpi = 300, width = 6, height = 4, units = "in")

p5<-ggplot(long5[], aes(x = value)) +
  geom_histogram(color="black", fill="white") +
  facet_wrap(~ name, scales = "free") +
  labs(x = "Micron Value", y = "Frequency")
#ggsave("animal-micron-length-spread5.jpg", plot = p5, dpi = 300, width = 6, height = 4, units = "in")
```
#### spread of each animal's micron lengths for dermis
```{r, spread-epi-pixel}
df_set1<-all_dermis_lengths_in_microns[,1:6]
df_set2<-all_dermis_lengths_in_microns[,7:12]
df_set3<-all_dermis_lengths_in_microns[,13:18]
df_set4<-all_dermis_lengths_in_microns[,19:24]
df_set5<-all_dermis_lengths_in_microns[,25:length(all_dermis_lengths_in_microns)]

# convert data to long format using tidyr::pivot_longer()
long1 <- tidyr::pivot_longer(df_set1, everything())
long2 <- tidyr::pivot_longer(df_set2, everything())
long3 <- tidyr::pivot_longer(df_set3, everything())
long4 <- tidyr::pivot_longer(df_set4, everything())
long5 <- tidyr::pivot_longer(df_set5, everything())

# plot using ggplot and facet_wrap()
p1<-ggplot(long1[], aes(x = value)) +
  geom_histogram(color="black", fill="white") +
  facet_wrap(~ name, scales = "free") +
  labs(x = "Micron Value", y = "Frequency")
p1
#ggsave("animal-derm-micron-length-spread1.jpg", plot = p1, dpi = 300, width = 6, height = 4, units = "in")

p2<-ggplot(long2[], aes(x = value)) +
  geom_histogram(color="black", fill="white") +
  facet_wrap(~ name, scales = "free") +
  labs(x = "Micron Value", y = "Frequency")
p2
#ggsave("animal-derm-micron-length-spread2.jpg", plot = p2, dpi = 300, width = 6, height = 4, units = "in")

p3<-ggplot(long3[], aes(x = value)) +
  geom_histogram(color="black", fill="white") +
  facet_wrap(~ name, scales = "free") +
  labs(x = "Micron Value", y = "Frequency")
#ggsave("animal-derm-micron-length-spread3.jpg", plot = p3, dpi = 300, width = 6, height = 4, units = "in")

p4<-ggplot(long4[], aes(x = value)) +
  geom_histogram(color="black", fill="white") +
  facet_wrap(~ name, scales = "free") +
  labs(x = "Micron Value", y = "Frequency")
#ggsave("animal-derm-micron-length-spread4.jpg", plot = p4, dpi = 300, width = 6, height = 4, units = "in")

p5<-ggplot(long5[], aes(x = value)) +
  geom_histogram(color="black", fill="white") +
  facet_wrap(~ name, scales = "free") +
  labs(x = "Micron Value", y = "Frequency")
#ggsave("animal-derm-micron-length-spread5.jpg", plot = p5, dpi = 300, width = 6, height = 4, units = "in")
```

### Write function to calculate average length for each column in epidermis and dermis dfs (aka each animal)
```{r, fnc-to-calcualte-averages}
# Define a function to calculate column-wise averages
calculate_averages <- function(data) {
  # Calculate column-wise averages using colMeans() function
  avg <- colMeans(data, na.rm = TRUE)
  
  # Create a new dataframe to store the column-wise averages
  avg_df <- data.frame(column = names(data), average = avg)
  
  # Return the new dataframe
  return(avg_df)
}

# The calculate_averages() function takes one argument data, which is the dataframe for which we want to calculate the column-wise averages.
# 
# The colMeans() function is used to calculate the column-wise averages of the dataframe. The na.rm = TRUE argument specifies that missing values should be removed before calculating the averages.
# 
# We then create a new dataframe avg_df to store the column names and their respective averages. The data.frame() function is used to create the new dataframe with two columns: "column" for the column names, and "average" for the column-wise averages.
# 
# Finally, we return the new dataframe avg_df from the function.
```

### Use previous function to create dataframes with averages for epidermis and dermis df's
```{r, calc-averages}
# Call the calculate_averages() function to calculate the column-wise averages
all_epidermis_in_microns_AVG <- calculate_averages(all_epidermis_lengths_in_microns)
colnames(all_epidermis_in_microns_AVG)<-c("filename", "average")
rownames(all_epidermis_in_microns_AVG)<-c(1:length(rownames(all_epidermis_in_microns_AVG)))

all_dermis_in_microns_AVG <- calculate_averages(all_dermis_lengths_in_microns)
colnames(all_dermis_in_microns_AVG)<-c("filename", "average")
rownames(all_dermis_in_microns_AVG)<-c(1:length(rownames(all_dermis_in_microns_AVG)))
```

### Visualize average micron lengths (per animal) for epidermis/dermis 
Use bar chart
```{r, viz-animal-pixel-averages}
categories <- c(letters[1:16], "r", "u", "v", "w", "x", "y", "z", "z1", "z10", "z2", "z4", "z6", "z8", "z9")

# for epidermis
df1<- cbind(all_epidermis_in_microns_AVG, categories)
p1<-ggplot(df1, aes(x = categories, y = all_epidermis_in_microns_AVG[,2])) +
  geom_bar(stat = "identity", color="black", fill="white") +
  xlab("Animal") +
  ylab("Average Length of Epidermis in microns")
p1

#ggsave("avg-epidermis-micron-length-by-animal.jpg", plot = p1, dpi = 300, width = 6, height = 4, units = "in")

# for dermis
df2<- cbind(all_dermis_in_microns_AVG, categories)
p2<-ggplot(df2, aes(x = categories, y = all_dermis_in_microns_AVG[,2])) +
  geom_bar(stat = "identity", color="black", fill="white") +
  xlab("Animal") +
  ylab("Average Length of Dermis in microns")
p2

#ggsave("avg-dermis-micron-length-by-animal.jpg", plot = p2, dpi = 300, width = 6, height = 4, units = "in")
```